---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# distionary

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/distionary)](https://CRAN.R-project.org/package=distionary)
[![Codecov test coverage](https://codecov.io/gh/vincenzocoia/distionary/branch/main/graph/badge.svg)](https://codecov.io/gh/vincenzocoia/distionary?branch=main)
[![R-CMD-check](https://github.com/vincenzocoia/distionary/workflows/R-CMD-check/badge.svg)](https://github.com/vincenzocoia/distionary/actions)
<!-- badges: end -->

The goal of distionary is to allow you to make and evaluate standard families of univariate probability distributions.

## Installation

distionary is not on CRAN yet. You can download the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("vincenzocoia/distionary")
```
## Example

```{r}
library(distionary)
```

We can make distributions from standard families, like beta and Poisson:

```{r}
(d_beta <- dst_beta(2, 4))
(d_pois <- dst_pois(1.2))
```

You can also make your own family of distributions (see the vignette). 

We can also make empirical distributions from data:

```{r}
x <- c(4.1, 2.3, 3.4, 5.5, 1.0, 6.8)
(d_emp <- dst_empirical(x))
```

We can evaluate different distributional forms, such as the density or pmf:

```{r}
eval_density(d_beta, at = c(0.1, 0.2))
eval_pmf(d_pois, at = c(1, 1.5, 3))
```

Or, we can enframe the results in a tibble:

```{r}
enframe_cdf(d_beta, d_pois, d_emp, at = c(0.1, 0.6, 1.5, 3))
```

Evaluate properties of the distributions:

```{r}
mean(d_beta)
skewness(d_pois)
range(d_emp)
```


## Code of Conduct

Please note that the distionary project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
